---
title: "runoff_volumes"
author: "Joe DeCesaro"
date: "8/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(janitor)
```

Source your storm_runoff.R script so you are able to use the predict_runoff function in your .Rmd
```{r}
source(here("src", "storm_runoff.R"))
```

In a code chunk in your runoff_volumes.Rmd, use your predict_runoff function to estimate stormwater volume for a watershed of 182 acres, over a range of estimates for the impervious fraction (from 0.6 to 0.8, by increments of 0.01). Note: you do not need to write a for loop here.
```{r}

runoff_vols <- predict_runoff(imperv_frac = seq(from = 0.6, to = 0.8, by = 0.01), watershed_area = 182)

```

Bind your sequence of impervious fractions together with the resulting runoff volume calculated into a data frame
```{r}
runoff_vols_df <- data.frame(ImperviousFractions = seq(from = 0.6, to = 0.8, by = 0.01), RunoffVolumes = runoff_vols)
```

Create a ggplot graph that has both dots and connecting lines (i.e., you’ll layer geom_point() and geom_line(). Update axis labels. Export a png of your graph to the figs folder using ggsave
```{r}
runoff_plot <- ggplot(data = runoff_vols_df, aes(x = ImperviousFractions, y = RunoffVolumes)) + 
  geom_point() +
  geom_line() +
  labs(x = "Impervious Fractions",
       y = "Runoff Volumes (ft^3)")
runoff_plot

ggsave(plot = runoff_plot, filename = here("figs", "runnoff_plot.png"))
```
done with Task 1

